---
output:
  word_document: default
  html_document: default
---
# Module 6 - Assignment 1
## Kip Harkey

### Libraries

```{r}
options(tidyverse.quiet=TRUE)
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
```

### Datasets

```{r}
library(readr)
trucks <- read_csv("trucks.csv")
```

### Task 1

```{r}
ggplot(trucks,aes(Distance,Speeding))+geom_point()
```

There appears to be clustering going in in the average distance traveled; two primary clusters near 50 miles and 175 miles. 

### Task 2

```{r}
trucks <- trucks %>% select(Distance,Speeding)
trucks2<-as.data.frame(scale(trucks))
```

### Task 3

```{r}
set.seed(64)
clusters <- kmeans(trucks2, 2)
fviz_cluster(clusters, trucks2)
```

 As observed in Task 1, there exists two clusters splitting the Distance variable.

###Task 4

```{r}
set.seed(64)
fviz_nbclust(trucks2, kmeans, method = "wss") 
```

 Another method  
```{r}
set.seed(64)
fviz_nbclust(trucks2, kmeans, method = "silhouette") 
```

 Both methods indicate that the ideal number of clusters is 4.

### Task 5

```{r}
set.seed(64)
clusters <- kmeans(trucks2, 4)
fviz_cluster(clusters, trucks2)
```
### Task 6

The clusters seem to break up the drivers into four quadrants:
  -Drivers traveling a short distance and are not speeding
  -Drivers traveling a long distance and are not speeding
  -Drivers traveling a short distance and are speeding
  -Drivers traveling a long distance and are speeding
  
  
```{r}
kenpom20 <- read_csv("kenpom20.csv")
```
  

###Task 7

```{r}
bball2 <- kenpom20 %>% select(-TeamName)
bball2<-as.data.frame(scale(bball2))
set.seed(123)
fviz_nbclust(bball2, kmeans, method = "wss") 
fviz_nbclust(bball2, kmeans, method = "silhouette") 
```

 There does not appear to be a consensus as to the number of clusters between the two methods.

### Task 8

```{r}
set.seed(1234)
clusters2 <- kmeans(bball2, 4)
fviz_cluster(clusters2, bball2)
```
### Task 9

```{r}
bball2 = bball2 %>% mutate(clusternum = clusters2$cluster)
ggplot(bball2,aes(AdjOE,AdjDE,color = factor(clusternum)))+geom_point()
```

 Clusters 1  and 3 appear to be centrally focused, whereas clusters 2 and 3 appear to be on either end of a negative correlation. 
